{\it E}nKCF: Ensemble of Kernelized Correlation Filters for Object Tracking in High Speed

### 2017-04-26 draft.tex
Abstract Edited

%%%%%%%%% ABSTRACT
\begin{abstract}
Computer vision technologies are very attractive for practical
application of embedded systems in that most of the embedded systems
already includes image acquisition pipeline and a tremendous amount of
progresses on research has been made. However, to successfully deploy
a computer vision algorithm on any existing embedded systems, a vision
algorithm needs to satisfy some criteria: minimal, manual intervention
after deployment and small footprint of computing resource consumption
and executable size. This criteria assumes the performance of the
algorithm is reasonably good. To this end, in this paper, we propose an
ensemble of the kernelized correlation filters (KCF), aka {\it E}nKCF,
for a single-target object tracking. In particular, we developed a
committee of KCFs to specifically address the scale-change and the
translation over frames. In addition, we devised a Bayes filter to
minimize the gap of interactions between KCFs. It is well known that
an online, model-free tracker like ours is prone to drift over
time. To cope with such drifts, we developed a re-detection module
that reliably identifies when to lose the target, hand-picks a small
number of object proposals from existing object proposal methods
(e.g., ``Edge Box''), and re-initializes the track to track the object
for a longer period. To verify the usefulness of the proposed method,
we compared the performance of ours to those of existing online
tracking methods. Experimental results showed that the performance of
our tracker are $72.53\%$ \textit{precision} at $20$ px, $52.90\%$ \textit{AUC} for OTB100 data
and $55.71\%$ and $41.71\%$ for UAV123 data. This confirmed that our tracker outperformed the existing high speed correlation filter based trackers about $5\%$ in terms of precision and $10\%$-$20\%$ in AUC. Finally,  our implementation ran at $340$ fps for OTB100 dataset and at $416$ fps for UAV123 dataset that is as fast as other correlation filter based trackers such as KCF ($292$ fps), DCF($457$ fps) and STC ($350$ fps) for UAV123.
\end{abstract}

>>>>

%%%%%%%%% ABSTRACT
\begin{abstract}
Computer vision technologies are very attractive for practical
application of embedded systems in that most of the embedded systems
already includes image acquisition pipeline and a tremendous amount of
progresses on research has been made. However, to successfully deploy
a computer vision algorithm on any existing embedded systems, a vision
algorithm needs to satisfy some criteria: minimal, manual intervention
after deployment and small footprint of computing resource consumption
and executable size. This criteria assumes the performance of the
algorithm is reasonably good. To this end, in this paper, we propose an
ensemble of the kernelized correlation filters (KCF), aka {\it E}nKCF,
for a single-target object tracking. In particular, we developed a
committee of KCFs to specifically address the scale-change and the
translation over frames. In addition, we devised a Bayes filter to
minimize the gap of interactions between KCFs. It is well known that
an online, model-free tracker like ours is prone to drift over
time. To cope with such drifts, we developed a re-detection module
that reliably identifies when to lose the target, hand-picks a small
number of object proposals from existing object proposal methods
(e.g., ``Edge Box''), and re-initializes the track to track the object
for a longer period. To verify the usefulness of the proposed method,
we compared the performance of ours to those of existing other online high speed
tracking methods. Experimental results showed that the performance of
our tracker are $72.53\%$ \textit{precision} at $20$ px, $52.90\%$ \textit{AUC} for OTB100 data
and $55.71\%$ and $41.71\%$ for UAV123 data. This confirmed that our tracker outperformed the existing high speed correlation filter based trackers about $5\%$ in precision and $10\%$-$20\%$ in AUC. Finally,  our implementation ran at $340$ fps for OTB100 dataset and at $416$ fps for UAV123 dataset that is as fast as other correlation filter based trackers such as KCF ($292$ fps), DCF($457$ fps) and STC ($350$ fps) for UAV123.
\end{abstract}
